---
title: "IDS 2935: Historical Narratives"
author: "Emilio M. Bruna"
date: "updated: `r Sys.Date()`"
mainfont: SourceSansPro
geometry: margin=1in
fontsize: 12pt
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[R]{last update `r Sys.Date()`}
- \fancyfoot[C]{ }
- \fancyhead[R]{Historical Narratives, p. \thepage}
- \fancyhead[L]{IDS 2935 - Rain Forests (`r format(Sys.time(), '%Y')`)}
- \usepackage[default]{sourcesanspro}
- \usepackage{parskip}
- \usepackage{xcolor}
- \AtBeginDocument{\let\maketitle\relax}
- \usepackage{sectsty} \sectionfont{\centering}
- \usepackage{titlesec}
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
- \usepackage{sectsty} \subsectionfont{\color{darkmidnightblue}}
- \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
output:
  pdf_document: default
  html_document:
    df_print: paged
  rmdformats::robobook: default
editor_options: 
  markdown: 
    wrap: 72
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```
# IDS 2935: Historical Narratives

## Before Class

1. Email Students class location, reminder to pring printed version of the historical narratives

## Bring to Class

1. Roster
2. Syllabi
3. Masks, Hand Sanitizer
4. Name cards & markers

## Pre-class Preparation (Students):

1. Bring printout of the Historical Narratives

### Assignments

### Readings/Videos: 

1. Historical Narratives 

## Objectives and Competencies:   

1. To explore the cultural and historical roots of contemporary conceptualizations of rain forests and the people that live in them.
1. To conduct basic text and sentiment analysis of the texts written by early European visitors to rain forests.
1. To use the results of these analyses to infer the major themes or narratives about rain forests and their people established by these historical texts

\newpage
```{r timer, echo=FALSE}

Block1_intro <- 5
Block1_breakout <- 10
Break <- 0
return_results <- 10
intro_next_session <- 15
questions <- 5  
  
total_time <- 
  Block1_intro + 
  Block1_breakout + 
  Break + 
  return_results + 
  questions +
  intro_next_session 


time_remain <- 150 - total_time
```
# Class Outline (Total Time: `r total_time` min)
\vspace{0.5cm}

### **Intro: ** (`r Block1_intro` min)

1. Most Europeans entered the tropics in a political and social climate of colonization and exploitation (of people, their culture, and natural resources). 
1. That shapes their perceptions of both tropical environments and the people they encountered.
1. These people wrote home about what they saw, and brought things back with them.  
1. These stories percolate through society and are reflected back by authors and artists for consumption by the public.
1. This reinforces and helps perpetuate the first perceptions (and misconceptions).

### **Breakout** (`r Block1_breakout` min): Text analysis

1. Text analysis assignment

### **Return and discuss breakout results** (`r return_results` min)

1. Review results of in-class text analysis

### **Break**  (`r Break` min)    

### **Breakout 2**  (`r intro_next_session` min)      

1. BE SURE TO DISCUSS RALEIGH PASSAGE: arguments about location of paradise and if it was under the equinoctal line.


### Closing Remarks/Questions (`r questions` min)

<!-- ### Free Time -->

<!-- There are `r time_remain` min remaining that can be used to answer questions -->
\vspace{1.5cm}
# Additional Resources and Reading Materials
\vspace{0.5cm}

[A Brief History of the Age of Exploration](https://www.thoughtco.com/age-of-exploration-1435006)

[European Exploration and Settlement in the New World](https://www.u-s-history.com/pages/h1031.html)
