---
title: 'Syllabus'
author: "Emilio M. Bruna"
date: "`r format(Sys.time(), '%Y')`"
web: www.BrunaLab.org
github: embruna
twitter: https://twitter.com/BrunaLab
phone: (352) 514-3935
email: embruna@ufl.edu
geometry: margin=1in
fontsize: 12pt
linkcolor: blue
urlcolor: blue
site: bookdown::bookdown_site
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \fancyhead[R]{Syllabus, p. \thepage}
- \fancyhead[L]{IDS 2935 - Rain Forests (`r format(Sys.time(), '%Y')`)}
- \usepackage[default]{sourcesanspro}
- \usepackage{parskip}
- \usepackage{xcolor}
- \AtBeginDocument{\let\maketitle\relax}
# - \usepackage{sectsty} \allsectionsfont{\raggedright}
- \usepackage{sectsty} \sectionfont{\centering}
- \usepackage{titlesec}
- \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
output: pdf_document
  # word_document: default
#   html_document
# weight: 5
    # df_print: paged
---

```{r setup_syllabus, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(tidyverse)
```

# The Future of Rain Forests
## IDS 2935 - Quest 2 - Fall 2022

\vspace{0.6cm} 

## Course Description & Information
\vspace{0.3cm} 

Tropical Rain Forests cover approximately 15% of the Earth’s land surface but contain over 50% of the world’s biodiversity. They are also the home to millions of people, the source of products central to our lives, shape global climate, and are being cleared at unprecedented rates. Students in this class will investigate the same fundamental questions asked by scientists that study rain forests: Why are we fascinated by rain forests? How have stereotypes about them permeated everything from pop culture to international relations? What gave rise to their remarkable biodiversity? What are the drivers and consequences of deforestation? Is rain forest conservation compatible with socioeconomic development? 

**By the end of the course students will be able to:**  

* Recognize and describe stereotypes about rain forests & their residents
* Analyze rain forest tropes in art, literature, & popular culture
* Discuss & evaluate hypotheses for the origins and maintenance of tropical biodiversity
* Explain & compare human history in rain forests
* Review contemporary threats to rain forests
* Analyze and visualize data on deforestation
* Review and contrast strategies for rain forest conservation & restoration
* Identify rain forests in their daily lives & set personal goals for advancing their conservation
* Produce materials for communicating about rain forests to family and peers

### Class Day, Time, & Location 

\vspace{0.3cm}
> **Tuesday Period 3** (9:35 - 10:25 AM) in LIT-0237 _and_  
> **Thursday Periods 3-4** (9:35 - 11:30 PM) in MAEB-0211. 

**Instructor:** Dr. Emilio M. Bruna  

<!-- \vspace{0.3cm} -->
<!-- &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Dr. Emilio M. Bruna**   -->

+ **email:** embruna@ufl.edu [email messages via the course Canvas page are preferred]
+ **Phone**: (352) 846-0634
+ **Office Location & Office Hours**: Wednesday and Friday 10:30 am - 12 noon in the Tropical Ecology & Conservation Lab, 711 Newell Drive (for a map to the lab click the "Contact" link at [BrunaLab.org](http://brunalab.org)). You can come to office hours in person or via Zoom (link on class canvas page). If you like, you _sign can up for a specific time slot in advance at [embruna.youcanbook.me](https://embruna.youcanbook.me)_. If you can't make it to Office Hours on those days/times let me know and we will find a time that works for you.  

**Teaching Assistant:** Thomas Smith
<!-- \vspace{0.3cm} -->
<!-- &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Thomas Smith**   -->

+ **email:** thomassmith@ufl.edu  [email via the course Canvas page is preferred]
+ **Office Location & Office Hours**: TBD in the Tropical Ecology & Conservation Lab (same location as Dr. Bruna)

### Reasons you should come to Office Hours.
\vspace{0.3cm}

  * Introduce yourself
  * _free tea, coffee, or espresso in our lab kitchen_
  * Ask for clarification on assignments
  * Discuss work we did in class to make sure you understood the key points
  * Get feedback on ideas for class projects
  * Ask questions about applying to graduate school
  * Ask for help arranging a study group
  * _You don't need a reason...just come on by._

**Required & Recommended Course Materials**: All course materials, including readings and videos, will be made available on the course Canvas page. However, many of the assigned articles from the New York Times have dynamic multimedia data visualizations and video that can't be appreciated in pdf format. _Students in this class should sign up for free online access to the NY Times by following the instructions at [this UF Libraries Website](https://businesslibrary.uflib.ufl.edu/c.php?g=943928&p=7708734)._

### **GenEd Information**  
\vspace{0.3cm}
* **Primary Designation**: Biological Sciences
* **Secondary Designation (if seeking)**: International (N)
* **Writing Designation**: None
* _A minimum grade of C is required for general education credit_
* More detailed GenEd and Quest Course Objectives/SLOs are in Section VIII


## Graded Coursework
\vspace{0.3cm} 
```{r assign, echo=FALSE,message = FALSE,warning=FALSE}
assignments <- read_csv("./assignments.csv") 

df2<- c("","","",sum(assignments$Points)) 
df2<-as.character(df2)
df2[4]<-paste("TOTAL = ",df2[4],sep="")
assignments <- rbind(assignments,df2)
assignments <-assignments %>% select(-Due)


# landscape()
# assignments[5, 3]<-cell_spec(assignments[6, 3], "latex",  align="c")
kable(assignments,
      # digits = 2,
      align="llc",
      format="latex",
      row.names = FALSE,
      escape= F,
      booktabs=T,
      linesep = "",
      ) %>% 
   kable_classic_2(full_width = T,
                latex_options="scale_down",
                font_size = 8,
                position = "left") %>% 
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "18em") %>%
  # column_spec(3, width = "5em") %>% 
  column_spec(3, width = "6em") %>% 
  row_spec(0,hline_after = F, bold=T) %>% 
  row_spec(c(1:5),hline_after = T) %>% 
  row_spec(6,bold=T) %>% 
  add_indent(6)

```

<!-- In-class assignments -->
<!-- 1. Day 1 Survey (Y/N Grade) -->
<!-- 1. Text Analysis - Historical -->
<!-- 1. Photo/Lit Analysis -->
<!-- 1. Video analysis: comparison of LLP and Tropical Forest structure  -->
<!-- 1. Photo Safari - FLMNH -->
<!-- 1. Diversity/Abundance Data Analysis -->
<!-- 1. Movie Bingo  (Y/N Grade) -->
<!-- 1. Geography Quiz  (Y/N Grade) -->
<!-- 1. PCE Violations -->
<!-- 1. (Relative) Species Diversity in Different Groups -->
<!-- 1. What is a forest?  (Y/N Grade) -->
<!-- 1. Durian Fest   (Y/N Grade) -->
<!-- 1. Rural Pop Data Analysis -->
<!-- 1. Community Conservation Negotiation  (Y/N Grade) -->
<!-- 1. Deforestation Data Analysis -->
<!-- 1. Palm Oil Stakeholder Analysis  (Y/N Grade) -->
<!-- 1. Show your stripes  (Y/N Grade) -->
<!-- 1. Q for Journalist  (Y/N Grade) -->
<!-- 1. En-roads Group Dashboard  (Y/N Grade) -->
<!-- 1. Conservation Values Survey  (Y/N Grade) -->
<!-- ### **Weekly Course Schedule**  -->
## Semester Overview & Key Dates
\vspace{0.1cm}
```{r course_calendar, echo=FALSE,message = FALSE,warning=FALSE}
calendar <- read_csv("./course_schedule_short.csv") %>% 
  # calendar <- calendar %>% 
  mutate(WEEK=paste(Week1,WEEK,sep=" ")) %>% 
  select(-X1,-Week1) %>% 
  mutate(DATE=paste(Day,Month,sep="-")) %>% 
  mutate(SESSION=as.character(SESSION)) %>% 
  select(WEEK,SESSION,DATE,TOPIC, `ASSIGNMENT DISTRIBUTED or DUE`) %>% 
  replace_na(list(DATE="",WEEK="",SESSION="", TOPIC="", `ASSIGNMENT DISTRIBUTED or DUE`="")) %>% 
  rename(" "="SESSION") 
  

calendar$WEEK <- gsub("NA NA","", calendar$WEEK)
calendar$DATE <- gsub("NA-NA","", calendar$DATE)
calendar$WEEK <- gsub("NA Final Exam","", calendar$WEEK)
calendar$WEEK <- gsub("Finals Week NA","Finals Week", calendar$WEEK)
# names(calendar) <- c("","","")

kable(calendar,
      # digits = 2,
      align="l",
      format="latex",
      row.names = FALSE,
      escape= TRUE,
      booktabs=T,
      linesep = "",
      ) %>% 
  kable_paper(full_width = ) %>%
  # column_spec(1, bold = F, border_right = T) %>%
  # column_spec(2, width = "5em", background = "white",border_right = T) %>% 
  pack_rows("WHY ARE WE FASCINATED BY TROPICAL RAIN FORESTS?", 1, 6) %>%
  pack_rows("THE ECOLOGY & EVOLUTION OF TROPICAL RAIN FORESTS", 7, 21) %>%
  pack_rows("THE DRIVERS AND IMPACTS OF DEFORESTATION", 22, 30) %>%
  pack_rows("THE FUTURE OF TROPICAL RAIN FORESTS", 31, 48) %>%
  # pack_rows("Finals Week", 49, 49) %>%
  kable_styling(bootstrap_options = c("hover"),
                full_width = T,
                latex_options="scale_down", 
                font_size = 8,
                position = "left") %>% 
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "1em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(4, width = "23em") %>% 
  column_spec(5, bold=T) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(49, bold=T) 
# column_spec(3, width = "15em") %>%
# column_spec(4, width = "3em") %>%
# row_spec(0,hline_after = F, bold=T) %>%
# row_spec(c(1:2),hline_after = T)

```
\newpage
# Assigned Reading/Viewing
\vspace{0.1cm}

**Please read or watch the assigned materials _before_ class.** The assignment for each session is subject to change based on current events; changes will be announced via Canvas.
\vspace{0.1cm}  

### WEEK 1-2:	Introductions & Historical Narratives
\vspace{0.2cm}
> Excerpts from Historical Narratives [[link to pdf](../IDS2935_class_sessions/02_trf_narratives/narratives_in_class/historical_narratives.pdf)]

<!-- * IN CLASS: Analysis of Historical Narratives -->

### WEEK 2-1	Rain forest imagery in Art & Literature
\vspace{0.2cm}
> Excepts from Poetry and Fiction [[link to pdf](../IDS2935_class_sessions/03_trf_culture/lit_poetry.pdf)]

<!-- * IN CLASS: (1) word cloud of survey (2) Analysis of Lit and Art -->

### WEEK 2-2 The Rain Forest in Pop Culture
\vspace{0.2cm}
> Jolly, Priscilla. 2021. ‘Godzilla vs. Kong’: Monster movies evoke adventure but also ‘dangers’ of tropics. *The Conversation.* [[link to read online](https://theconversation.com/godzilla-vs-kong-monster-movies-evoke-adventure-but-also-dangers-of-tropics-158105)]

<!-- * IN CLASS: Movie sign-up and assignment hand out -->

<!-- AND -->

<!-- * IN CLASS: Guest Lecture -->	   


### WEEK 3-1	What is a Rain Forest? 
\vspace{0.2cm}
> Why does Earth have Deserts? [[link to video](https://www.youtube.com/watch?v=T6Us1sPXBfA)]

<!-- * IN CLASS: Comparison of Forests with 360 Videos-->
<!-- 2. [Longleaf Pine Forest](https://www.youtube.com/watch?v=kRD1CpQOF7Q&t=17s) -->
<!-- 3. [CI: Under the Canopy](https://www.youtube.com/watch?v=5JvJCvdqvYs) -->

### WEEK 3-2	What is a Rain Forest? (cont.)
\vspace{0.2cm}
> None

<!-- * IN CLASS: Geography Quiz Bowl -->

### WEEK 4-1	Patterns of Biodiversity
\vspace{0.2cm}
> Why Are There So Many Species Near the Equator? [link to video](https://www.youtube.com/watch?v=IrbKix96_k0)

<!-- * IN CLASS: Species-Abundance Data Analysis -->

### WEEK 4-2	Coevolution & the origins of tropical biodiversity
\vspace{0.2cm}
> Is this the biggest flower in the world? "BBC Earth: Corpse Flower Stinks of Death" [[link to video](https://www.youtube.com/watch?v=YxIpl38rsMo)]. (A slightly less dramatic video in which you can get a better idea of the flower's size is [[here](https://www.youtube.com/watch?v=0cGRujABwuQ)]  

> Or maybe it's this one: The Titan arum [[link to video](https://www.youtube.com/watch?v=5Jg-GlCXpEI)]  

> An introduction to Army Ants: [[link to video](https://www.youtube.com/watch?v=p16g5IVCdeE)]  

> **_Optional:_** A more sophisticated (but actually less complete) overview is offered by the BBC: [[link to video](https://www.youtube.com/watch?v=JsfiUR0ZzLw)]  

> **_Optional:_** A closer look at the Army Ant Birds: [[link to video](https://www.youtube.com/watch?v=SQPcIYV_vKM)]  

<!-- * IN CLASS: FLMNH Photo Safari  -->

### WEEK 5-1	Forest disturbance, dynamics, & the maintenance of diversity
\vspace{0.2cm}
> None  

<!-- include Terra Preta and Rain Forest Manipulation  -->

### WEEK 5-2	Forest disturbance, dynamics, & the maintenance of diversity
\vspace{0.2cm}
> None   

<!-- * IN CLASS: PCE Violations in the Tropics -->

### WEEK 6-1	The Paradox of Luxuriance
\vspace{0.2cm}
> None  

<!-- * IN CLASS: Geography Quiz -->


### WEEK 6-2	Humans are part of rain forests  
\vspace{0.2cm}

> Langewiesche, William. 2022. "The War for the Rainforest." _NY Times_. [[read online](https://www.nytimes.com/2022/03/16/magazine/amazon-rainforest-ituna-itata.html)]   

<!-- * IN CLASS: Data Analysis: Rural-Urban -->
			
### WEEK 7-1	Narratives Revisited: Biology, History, Fiction, Reality
\vspace{0.2cm}
> Anthony Bourdain's Parts Unknown: Congo (S1E8) [[link to video](https://www.imdb.com/title/tt2849384/)]  

> Bourdain's Field Notes: Congo [[read online](https://explorepartsunknown.com/congo/bourdains-field-notes-congo/)]  

> NPR's Throughline Podcast: "There Will Be Bananas" [[listen online](https://www.npr.org/2020/01/07/794302086/there-will-be-bananas)]  
  

<!-- * IN CLASS: Discussion of Movie Tropes / Reviews -->

### WEEK 7-2	JUNGLE FILM FESTIVAL 2022
\vspace{0.2cm}
> None  

<!-- * IN CLASS: FILM FESTIVAL -->
<!-- * IN CLASS: Movie Options: Congo, The Rundown, Jungle Cruise, Blood Monkey, Romancing the Stone, The Jungle (D Radcliffe) -->

### WEEK 8-1	Forest cover and forest loss I
\vspace{0.2cm}
> Nolen, Stephanie (Reporting) with Elkaim, Aaron Vincent (Photographs).  2018. "Inside the Amazon’s Deforestation Crisis". _The Globe and Mail_. [[read online](https://www.theglobeandmail.com/news/world/amazon-rainforest-deforestation-crisis/article37722932/)]. 

### WEEK 8-2	Forest cover and forest loss II  

> Searcey, Dionne (reporting) and Gilbertson, Ashley (photographs). 2022 "Raft by Raft, a Rainforest Loses Its Trees" _NY Times_. [[read online](https://www.nytimes.com/interactive/2022/06/14/climate/congo-rainforest-logging.html)]

<!-- * IN CLASS: Download and Analysis of Forest Loss Data  -->

### WEEK 9-1	Drivers & Consequences of Deforestation I: Mining, Timber, Fire, Infrastructure
\vspace{0.2cm}
> Andreoni, Manuela, Blacki Migliozzi, Pablo Robles and Denise Lu. Photographs by Victor Moriyama. 2022. "The Illegal Airstrips Bringing Toxic Mining to Brazil’s Indigenous Land". _NY Times_. [[read online](https://www.nytimes.com/interactive/2022/08/02/world/americas/brazil-airstrips-illegal-mining.html)]  

> Andreoni, Manuela. 2022. "Stopping wildfires before they start". _NY Times_. [[read online](https://www.nytimes.com/2022/07/26/climate/wildfires-brazil.html)]
 
 
### WEEK 9-2	Drivers & Consequences of Deforestation II: Agriculture  
\vspace{0.2cm}
> Devouring the Rain Forest. _Washington Post_. [[read online](https://www.washingtonpost.com/world/interactive/2022/amazon-beef-deforestation-brazil/)]  

> Robles, Pablo, Anuradha Raghu, Adam Majendie and Jin Wu 2021. "The World's Addiction to Palm Oil Is Only Getting Worse". _Bloomberg News_.  [[read online](https://www.bloomberg.com/graphics/2021-palm-oil-deforestation-climate-change/)]  

<!-- 1. Lustgarten, Abrahm. 2018. "Palm Oil Was Supposed to Help Save the Planet. Instead It Unleashed a Catastrophe". _NY Times_. [read online](https://www.nytimes.com/2018/11/20/magazine/palm-oil-borneo-climate-catastrophe.html) -->  

> Mason, Margie & McDowell, Robin. 2020. "Palm oil labor abuses linked to world’s top brands, banks". _Associated Press_. [[read online](https://apnews.com/article/virus-outbreak-only-on-ap-indonesia-financial-markets-malaysia-7b634596270cc6aa7578a062a30423bb)]  

> Beech, Hannah. 2019. One Casualty of the Palm Oil Industry: An Orangutan Mother, Shot 74 Times. _NY Times_. [[read online](https://www.nytimes.com/2019/06/29/world/asia/orangutan-indonesia-palm-oil.html)]  

<!-- * IN CLASS: Palm Oil Stakeholder Analysis -->

### WEEK 10-1	Climate change
\vspace{0.2cm}
> BBC News: Amazon rainforest: 'Once it's gone, it's gone forever' (interview with Erika Berenguer). [[link to video](https://www.youtube.com/watch?v=TigV80hwebg)]

<!-- * IN CLASS: Show Your Stripes -->

### WEEK 10-2	Climate change (cont.)
\vspace{0.2cm}
<!-- > Author. 2020. "The Congo rainforest is losing ability to absorb carbon dioxide. That’s bad for climate change". _Washington Post_. [[read online](https://www.washingtonpost.com/climate-environment/the-congo-rainforest-is-losing-its-ability-to-absorb-carbon-dioxide-thats-bad-for-climate-change/2020/03/03/3363d218-5ca9-11ea-9055-5fa12981bbbf_story.html)]    -->

> Pearce, Fred. 2018. "Rivers in the Sky: How Deforestation Is Affecting Global Water Cycles."  _Yale360_. [[read online](https://e360.yale.edu/features/how-deforestation-affecting-global-water-cycles-climate-change)]  

<!-- > Fisher, Max. 2019. "‘It’s Really Close’: How the Amazon Rainforest Could Self-Destruct" _NY Times_. [[read online](https://www.nytimes.com/2019/08/30/world/americas/amazon-rainforest-fires-climate.html)]   -->

<!-- > Chad Frischmann's Ted Talk: "100 solutions to reverse global warming"  [[link to video](https://www.ted.com/talks/chad_frischmann_100_solutions_to_reverse_global_warming?language=en)]   -->

<!-- > Climate Action Tracker Ted Talk: "The State of the Climate Crisis in 2021" [[link to video](https://www.ted.com/talks/climate_action_tracker_the_state_of_the_climate_crisis_in_2021?language=en)]   -->

> Serkez, Yaryna. 2020. Every Place Under threat. _NY Times_.  [[read online](https://www.nytimes.com/interactive/2020/10/02/opinion/amazon-under-threat.html)]  

> **_Optional:_** learn about the EN-ROADS simulator we will be using in class at this [[link to website](https://www.climateinteractive.org/en-roads/)]. You can even start experimenting with it here: [[link to site](https://en-roads.climateinteractive.org/scenario.html?v=22.8.0)]  

<!-- * IN CLASS: EN-ROADS Climate Simulation -->

### WEEK 11-1	Consumer choices
\vspace{0.2cm}
> Carodenuto, Sophia. 2021. "Chocolate fix: How the cocoa industry could end deforestation in West Africa".  _The Conversation_. [[read online](https://theconversation.com/chocolate-fix-how-the-cocoa-industry-could-end-deforestation-in-west-africa-161953)]  

> Lawal,Shola. 2020. "Our Endless Appetite For Chocolate Has Bitter Environmental Consequences" _Huffington Post_. [[read online](https://tinyurl.com/y6curgmn)]. 

> Hunt, Chris and Premathilake, Rathnasiri. 2018. "Prehistoric people started to spread domesticated bananas across the world 6,000 years ago." _The Conversation_. [[read online](https://theconversation.com/prehistoric-people-started-to-spread-domesticated-bananas-across-the-world-6-000-years-ago-99547)]  

> **_Optional:_** Mufson, Steven and Georges, Salwan. 2019. "The trouble with chocolate"  _Washington Post_ [[read online](https://www.washingtonpost.com/graphics/2019/national/climate-environment/mars-chocolate-deforestation-climate-change-west-africa/)] _amazing maps, pictures, and data visualizations_.  

> **_Optional:_** Williams, Wyatt. 2021. "How Your Cup of Coffee Is Clearing the Jungle". _NY Times_. [[read online](https://www.nytimes.com/2021/08/11/magazine/indonesia-rainforest-coffee.html)] _Longer, but really gripping and the article includes a link to an audio version if you prefer to listen to it_.


### WEEK 11-2	DURIAN FEST 2022
\vspace{0.2cm}
> Weintraub, Karen. 2019. "They’re Smelly and Spiky, and They Need Bats to Pollinate Them". _NY Times_. [[read online](https://www.nytimes.com/2019/12/04/science/bats-durians-indonesia.html)]  

> Wharton, Rachel. 2020. How the Tip of Florida Became a Tropical-Fruit Paradise. _Atlas Obscura_. [[read online](https://www.atlasobscura.com/articles/tropical-fruit-farms-in-united-states)]

> Frías, Carlos. 2022. "Oddly colored and somewhat phallic: How Miami’s rare tropical fruit went TikTok viral." _Miami Herald_. [[read online](https://www.miamiherald.com/miami-com/restaurants/article263608093.html#storylink=cpyhttps://www.miamiherald.com/miami-com/restaurants/article263608093.html)]  


<!-- > [How to make chocolate from scratch](https://twitter.com/fastworkers6/status/1557051342010535937?s=12&t=y5HmpXelWYe3mvVYNErbPQ)  -->
<!-- Need to find the original creator to credit properly -->


<!-- * IN CLASS: DURIAN FEST & Taste testing Tropical Fruits -->

### WEEK 12-1	International frameworks
\vspace{0.2cm}
> None 

### WEEK 12-2	Local Initiatives, Empowered Communities, & Activism
\vspace{0.2cm}
<!-- _Some inspiring evidence we can actually restore rain forests in a way that benefits local people, biodiversity, and the broader world via impacts on ecosystem services:_ -->

> Ruth Maclean (reporting, writing), Caleb Kabanda (reporting), and Nanna Heitmann (photography). 2022. "What do the protectors of Congo's peatlands get in return?" _NY Times_. [[read online](https://www.nytimes.com/interactive/2022/02/21/headway/peatlands-congo-climate-change.html)]   

> Kimbrough, L. 2021. "How settlers, scientists, and a women-led industry saved Brazil’s rarest primate". _Mongabay.com_ [[read online](https://news.mongabay.com/2021/05/how-settlers-scientists-and-a-women-led-industry-saved-brazils-rarest-primate/)].  

<!-- > "A vanishing forest reborn."[[read online](https://www.rolex.org/rolex-awards/milestones/environment/laury-cullen-jr)] (some great drone footage of the location in the story above and more about Laury Cullen's efforts [[read online](https://www.rolex.org/rolex-awards/milestones/environment/laury-cullen-jr)]   -->

> Don't underestimate what one person can do on their own: "BBC World Service: The man who grew his own rainforest" [[link to video](https://www.youtube.com/watch?v=AngaeIf78AQ)] _(keep an eye out for the Euglossine bees we learned about earlier in the semester...you can see them collecting scented oil from flowers at 2:04)._  

> Arellano, Astrid and Sierra Praeli, Yvette. 2022.  "A look at violence and conflict over Indigenous lands in nine Latin American countries". _Mongabay.com_
. [[read online](https://news.mongabay.com/2022/05/a-look-at-violence-and-conflict-over-indigenous-lands-in-nine-latin-american-countries/?utm_medium=Social&utm_source=Twitter#Echobox=1654027741-1)]  

<!-- * IN CLASS: Guest Speaker, Get Involved Fair -->

### WEEK 13-1	Protected areas
\vspace{0.2cm}
> Dasgupta, Shreya (with research by Annika Schlemm & Zuzana Burivalova). 2017. "Do protected areas work in the tropics?" Mongabay.com. [[read online](https://news.mongabay.com/2017/12/do-protected-areas-work-in-the-tropics/)]  


### WEEK 13-2	Forest restoration & regeneration
\vspace{0.2cm}
> Medici, Patricia. 2015 TED Fellows Talk. "The coolest animal you know nothing about...and how we can save it". [[link to video](https://www.ted.com/talks/patricia_medici_the_coolest_animal_you_know_nothing_about_and_how_we_can_save_it#t-694653)]  

> "Do tapirs defecate in the woods?" 2019. _The Economist_ [[read online](https://www.economist.com/science-and-technology/2019/04/17/do-tapirs-defecate-in-the-woods)]  

> Come prepared to make some money: we're looking into the economic benefits of setting aside land (or not) for conservation. To prepare, look this document over before class, it should take ~10 minutes max.: externalities and game intro.  

<!-- * IN CLASS: Land Conservation Game -->

### WEEK 14-1	Project Work Day 
\vspace{0.2cm}
> None  

### WEEK 14-2	No class: Thanksgiving Holiday  
\vspace{0.2cm}
> None    
  
### WEEK 15-1	Tropical Rain Forests and Global Health
\vspace{0.2cm}
> Lavinas Picq, Manuela 2020. "Spreading Faith, and Disease". _NY Times_. [[read online](https://www.nytimes.com/2020/10/02/opinion/amazon-missionaries-tribes-disease.html)]  

> Vittor, Amy, Gabriel Zorello Laporta, and Maria Anice Mureb Sallum. 2020. How deforestation helps deadly viruses jump from animals to humans. _The Conversation_. [[read online](https://theconversation.com/how-deforestation-helps-deadly-viruses-jump-from-animals-to-humans-139645)]

> Kuchipudi, Suresh V. 2020. Why so many epidemics originate in Asia and Africa – and why we can expect more. _The Conversation_. [[read online](https://theconversation.com/why-so-many-epidemics-originate-in-asia-and-africa-and-why-we-can-expect-more-131657)]

<!-- > Kaufman, Les. 2020. 0Reducing deforestation of tropical forests and supporting the communities that live there can reduce the risk of future pandemics. AFP via Getty Images -->
<!-- Video: Slowing deforestation is the key to preventing the next pandemic – but what does that cost? _The Conversation_ [[read online](https://theconversation.com/video-slowing-deforestation-is-the-key-to-preventing-the-next-pandemic-but-what-does-that-cost-143411)] -->


### WEEK 15-2	Rain Forest Headlines  
\vspace{0.2cm}
> Nicas, Jack (reporting) and Moriyama,Victor (Photos, Video). 2022. Inside the Amazon Journey That Left a Journalist and an Activist Dead. _NY Times._ [[read online](https://www.nytimes.com/interactive/2022/07/11/world/americas/amazon-murder-dom-phillips-bruno-pereira.html?smid=tw-nytimes&smtyp=cur)]  

<!-- * IN CLASS: Guest Speaker -->

### WEEK 16-1	What will we do?
\vspace{0.2cm}

> none

<!-- > Conservation Attitudes Survey: [[link to survey](http://go-fox.web-supported-production.linode.unep-wcmc.org/surveys/OTNQwqEWUb88CHA0BTOBYw/responses/new)]   -->

<!-- "tell me (1-2 sentences) what you thought of the results - did you find them surprising? Or do they make sense in terms of your philosophy about nature and its value to society?" -->

<!-- * IN CLASS: CLASS PROJECT FAIR -->

## Grading, Attendance, and Participation
\vspace{0.3cm} 
Requirements for class attendance and make-up exams, assignments, and other work in this course are consistent with university policies that can be found at: https://catalog.ufl.edu/UGRD/academic-regulations/attendance-policies/  

**Attendance:** Though attendance is not required, many of the sessions we we will be completing activities in class that count towards your grade. Most of these can be completed independently, but by doing them in class you will benefit from working collaboratively with the other students. _Some of the in-class activities, however, can not be completed on your own._ If you miss class on one one of these days, you can elect to make up the lost points with extra-credit assignments.  **_If you need to miss class for any reason, please let me know as soon as possible_**. We will make arrangements for you to complete any assignments and go over any material you will be missing. I would much rather you focus on your health, attend your conference, or support friends and family in need than struggle to turn in assignments. 

**Participation:** Consistent informed, thoughtful, and considerate class participation is encouraged (and in some cases required). If you have personal issues that prohibit you from joining freely in class discussion, e.g., shyness, language barriers, etc., that is not a problem. Please me know me as soon as possible and we will discuss alternative modes of participation.  

**Grade Assignment** (based on % of possible points):

\vspace{0.3cm}
> A = 94–100%, A- = 90–93%  
> B+ = 87–89%, B = 84–86%, B- = 80–83%  
> C+ = 77–79%, C = 74–76%, C- = 70–73%   
> D+ = 67–69%, D = 64–66%, D- = 60–63%  
> E	< 60  

**Regrades:** Requests for re-evaluation of any quizzes, exams, or assignments will only be considered if accompanied by a letter explaining why you think you deserve additional credit and the number of additional points you think you deserve.  The deadline for submitting these requests is one week after the work has been returned.

**Grade Points:** For information on how UF assigns grade points, visit: https://catalog.ufl.edu/UGRD/academic-regulations/grades-grading-policies/
    
<!-- ## Quest Learning Experiences -->
<!-- \vspace{0.3cm}  -->
<!-- **Experiential Learning Component**: This course has multiple experiential learning activities, including a field trip to the FLMNH Butterfly Rain Forest, home surveys of tropical products, and the gathering and analysis of data on deforestation and biodiversity in different tropical rain forest regions.  -->

<!-- **Self-Reflection Component**: Students will also have multiple opportunities for self-reflection throughout the course. In addition to reflection on their goals and expectations for the class, they will consider the (almost certainly under-appreciated) ubiquity of products derived from tropical plants and animals in their daily lives. Finally, they will have the opportunity to consider what actions they can take as individuals to advance rain forest conservation and the well-being of forest-dependent people. -->

## COVID-19 Statement
\vspace{0.3cm}
It's not over, people. Things will to continue to be unpredictable as new variants emerge, and . As such, situations may arise during the semester that complicate course participation (for students) or instruction (for the TA or Professor). If you are affected in any way by Covid-19, let us know so we can plan accordingly. You should not come to class if you suspect having contracted Covid-19 or are ill; just let us know and we'll work something out. Finally, please be respectful of others and their health decisions or needs. Mask use is still recommended by UF, as is vaccination. More guidance can be found at the CDC website (https://www.cdc.gov/media/releases/2022/p0811-covid-guidance.html) and the UF Covid Resources Page (https://coronavirus.ufl.edu/)

## Other Course Policies
\vspace{0.3cm}
**Children in the Classroom:** UF does not have a formal policy on children in the classroom. The policy described below reflects my commitment to student-parents.  

* **You and your nursing baby are welcome in class anytime.** I never want students to feel like they have to choose between feeding their baby and continuing their education. 
* **Occasionally bringing a child to class because of a gap in care is perfectly acceptable.** I understand that minor illnesses and unforeseen disruptions in childcare often put parents in the position of having to chose between attending class or staying home to care for them. Let me know in advance if at all possible.
* **If you bring your child to class:** Please sit close to the exit so that if your child needs attention you can more easily step outside until their needs have been met (and so other students can continue learning). Non-parents in the class, I ask that you please be willing to offer your seat near a door to parents as needed.
* **Let me know how i can help.** Finally, I understand that balancing school, childcare and perhaps even a job can be exhausting and a barrier to learning. I maintain the same high expectations for all students in my class, and will work with you to find ways you can balance your responsibilities as a parent and student.

**Materials and Supplies Fees**: There are no additional fees for this course. 

**Students Requiring Accommodation**: Students with disabilities or learning barriers that would like to request academic accommodations should connect with the Disability Resource Center by visiting https://disability.ufl.edu/students/get-started/. Please share your letter with me and discuss access needs as early as possible in the semester so that I can do whatever is necessary to ensure your participation and learning.

**UF Evaluations Process**: Students are expected to provide professional and respectful feedback on the quality of instruction in this course by completing course evaluations online via GatorEvals. Guidance on how to give feedback in a professional and respectful manner is available at https://gatorevals.aa.ufl.edu/students/. Students will be notified when the evaluation period opens, and can complete evaluations through the email they receive from GatorEvals, in their Canvas course menu under GatorEvals, or via https://ufl.bluera.com/ufl/. Summaries of course evaluation results are available to students at https://gatorevals.aa.ufl.edu/public-results/.

**University Honesty Policy**: UF students are bound by The Honor Pledge which states, “We, the members of the University of Florida community, pledge to hold ourselves and our peers to the highest standards of honor and integrity by abiding by the Honor Code. On all work submitted for credit by students at the University of Florida, the following pledge is either required or implied: “On my honor, I have neither given nor received unauthorized aid in doing this assignment.” The Honor Code (https://www.dso.ufl.edu/sccr/process/student-conduct-honor-code/) specifies a number of behaviors that are in violation of this code and the possible sanctions. Furthermore, you are obligated to report any condition that facilitates academic misconduct to appropriate personnel. If you have questions or concerns, consult with the instructor or TAs.  

### **In-Class Recording**
\vspace{0.3cm} 
+ **Students are allowed to record video or audio of class lectures. However, the purposes for which these recordings may be used are strictly controlled.** The only allowable purposes are (1) for personal educational use, (2) in connection with a complaint to the university, or (3) as evidence in, or in preparation for, a criminal or civil proceeding. All other purposes are prohibited. Specifically, students may not publish recorded lectures without the written consent of the instructor. 

+ **A “class lecture” is:** an educational presentation intended to inform or teach enrolled students about a particular subject, including any instructor-led discussions that form part of the presentation, and delivered by any instructor hired or appointed by the University, or by a guest instructor, as part of a University of Florida course. A class lecture does not include lab sessions, student presentations, clinical presentations such as patient history, academic exercises involving solely student participation, assessments (quizzes, tests, exams), field trips, private conversations between students in the class or between a student and the faculty or lecturer during a class session. 

+ **Publication without permission of the instructor is prohibited.** To “publish” means to share, transmit, circulate, distribute, or provide access to a recording, regardless of format or medium, to another person (or persons), including but not limited to another student within the same class section. Additionally, a recording, or transcript of a recording, is considered published if it is posted on or uploaded to, in whole or in part, any media platform, including but not limited to social media, book, magazine, newspaper, leaflet, or third-party note/tutoring services. A student who publishes a recording without written consent may be subject to a civil cause of action instituted by a person injured by the publication and/or discipline under UF Regulation 4.040 Student Honor Code and Student Conduct Code


## UF Resources 
\vspace{0.3cm} 

### **Counseling and Wellness Center**
\vspace{0.3cm}
* U Matter, We Care: If you or someone you know is in distress, please contact umatter@ufl.edu, 352-392-1575, or visit [U Matter, We Care website](https://umatter.ufl.edu/) to refer or report a concern and a team member will reach out to the student in distress.
    
* Counseling and Wellness Center: Visit the [Counseling and Wellness Center website](https://counseling.ufl.edu/) or call 352-392-1575 for information on crisis services as well as non-crisis services. 

* Student Health Care Center: Call 352-392-1161 for 24/7 information to help you find the care you need, or visit the [Student Health Care Center website](https://shcc.ufl.edu/). 

* University Police Department: Visit [UF Police Department website](https://police.ufl.edu/) or call 352-392-1111 (or 9-1-1 for emergencies). 

* UF Health Shands Emergency Room / Trauma Center: For immediate medical care call 352-733-0111 or go to the emergency room at 1515 SW Archer Road, Gainesville, FL 32608; Visit the [UF Health Emergency Room and Trauma Center website](https://ufhealth.org/emergency-room-trauma-center).

**Field and Fork Pantry**: The Hitchcock Pantry can provide food and toiletries for students experiencing food insecurity.  https://pantry.fieldandfork.ufl.edu/.

**The Writing Studio**: The writing studio is committed to helping University of Florida students meet their academic and professional goals by becoming better writers. Visit the writing studio online at http://writing.ufl.edu/writing-studio/ or in 2215 Turlington Hall for one-on-one consultations and workshops.  

## General Education and Quest SLOs/Objectives
<!-- \vspace{0.3cm}  -->
<!-- **Course Objectives — GenEd Primary Area & Quest ** -->

<!-- **Course Student Learning Outcomes (SLOs) — GenEd Primary Area & Quest ** -->

<!-- **Secondary Objectives and SLOs (Optional)** -->

<!-- * International Objectives (for N co-designation) -->

<!-- * International Student Learning Outcomes (for N co-designation) -->

