---
title: "Assignment 1 - Movie Reviews"
author: "Emilio M. Bruna"
date: "`r format(Sys.time(), '%Y')`"
web: www.BrunaLab.org
github: embruna
twitter: https://twitter.com/BrunaLab
phone: (352) 514-3935
email: embruna@ufl.edu
geometry: margin=1in
fontsize: 12pt
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
site: bookdown::bookdown_site
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \fancyhead[R]{Tropical Tropes in Film , p. \thepage}
- \fancyhead[L]{IDS 2935 - Rain Forests (`r format(Sys.time(), '%Y')`)}
- \usepackage[default]{sourcesanspro}
- \usepackage{parskip}
- \usepackage{xcolor}
- \usepackage{lscape}
- \AtBeginDocument{\let\maketitle\relax}
# - \usepackage{sectsty} \allsectionsfont{\raggedright}
- \usepackage{sectsty} \sectionfont{\centering}
- \usepackage{titlesec}
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
- \usepackage{sectsty} \subsectionfont{\centering\color{darkmidnightblue}}
- \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
always_allow_html: true
# classoption: landscape
output: pdf_document
# output: html_document
  # word_document: default
# output: html_document
# weight: 5
    # df_print: paged
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile,
  encoding = encoding,
  output_dir = "./static/uploads")
  })
---


```{r setup_syllabus, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(here)
```


### UPDATE BASED ON CONVERSTION WITH ED SPECIALIST - UFL

in-class - compare sets of movies, id theme, extract tropes, compare across and relate backl to reading

AND 

project



1. chose the two movies as either opposites (good depiction/bad depiction) or reinforcesrs (same tropes in different movies)
1. Reviewing Trailers might be a good in class activity because they are short and will have many of the same elements
1. Perhaps focus on a more limited set of tropes (10-15) and have them fill out for the entire movie (so people don't quit after getting the ten they need).
1. untapped opportunity to preview future aspects of the course (e.g., ask questions as part of assignment such as 'how do does this make you feel about conservation", or "what biodiversity / types of species do you see (or hear)  in forests")
1. She liked the idea of how quantifying how "trope-ey" the movies were. One possibility of a class activity afterwards would be to put movies on a gradient of trope-iness, perahps with some discussion about themovies we all saw and then students can place the one they chose to watch on a gradient. Maybe to get at this have people fill out a matrix in which they fill out some information about the movies (how they depict people, situations, the forest, etc). they can use the "index score" to rank their movies. In class the students can explain to the other styiudents why they put the movie they watched on the axis. 
1. Check out Jigsaw technique as a possibility for in class work: https://www.jigsaw.org/
1. No more "review" essay: instead make it short answer and in-class work. 



# Tropical Tropes in Film 
\vspace{0.5cm}
## Assignment Overview
\vspace{0.3cm}
Your assignment is to watch **three** films set in tropical rain forests and record how the rain forest setting is presented and advances the films' narrative. Note that is _not_ a summary of the film and its plot (i.e., a *descriptive review*) or an overall judgment of whether the film is "good" or "bad" (i.e., an *evaluative review*). **For each film need to do the following:** 

1. Document the tropes about rain forests used in each film (using the _Trope Checklist_)

> * Trope Checklist as an [MS Excel File](https://ids2935.netlify.app/uploads/trope_datasheet.xlsx) or as a [pdf file](https://ids2935.netlify.app/uploads/trope_datasheet.pdf). **IMPORTANT**: please enter the time stamp for each event in the following format: hh:mm:ss (i.e., at 3 minutes and 29 seconds would be: 00:03:29, at one hour, 12 minutes, and three seconds would be 01:12:03). Also, please do not add any lines with additional information to the excel file.  
> * List and definitions of Tropical Movie Tropes [pdf file](https://ids2935.netlify.app/uploads/movie_tropes.pdf). 

1. Explain how each film's use of these tropes _reinforces_ or _subverts_ one or more of the historical stereotypes about rain forests and the people that live in them that we discussed in class. Support your claims with specific examples drawn from these major elements:  

<!-- 1. Describe how the rain forest setting underscores each film's major themes -->
> * **Plot**: the narrative, setting, key events, action sequences, resolution, plausibility, themes, cultural context, etc. 
> * **Characters**: professions, personality, motivation, interactions, response to rain forest setting, etc.
> * **Visuals**: scenery, flora & fauna, props, wardrobe, shots, perspective, lighting, editing, effects, etc.
> * **Sound**: use and timing of background sounds (or silence), score, animal sounds, songs, etc.


## Films to Review
\vspace{0.3cm}

1. _**The African Queen**_ (1951): In WWI East Africa, a gin-swilling Canadian riverboat captain is persuaded by a strait-laced English missionary to undertake a trip up a treacherous river and use his boat to attack a German gunship. _(Starring Humphrey Bogart & Katharine Hepburn; Directed by John Huston)_. See the [[movie list]](https://ids2935.netlify.app/uploads/movie_list.pdf) for where to access this film.

2. _**Anaconda**_ (1997): When a documentary crew traveling through the Amazon jungle picks up a stranded man, they have no idea it will lead them face-to-face with the world's largest - and deadliest - snake. _(Starring Jon Voight, Jennifer Lopez, Eric Stoltz, Ice Cube, and Owen Wilson; Directed by Luis Llosa)_. See the [[movie list]](https://ids2935.netlify.app/uploads/movie_list.pdf) for where to access this film.

3. **One movie of your choice from [this [list]](https://ids2935.netlify.app/uploads/movie_list.pdf).**

<!-- 1. _Aguirre, Wrath of God_ (1972, directed by Werner Herzog, Rotten Tomatoes: 96%) -->
<!-- 1. _Apocalypse Now_ (1979, Directed by Francis Ford Coppola) -->
<!-- 1. _The Emerald Forest_ (1985, Directed by John Boorman) -->

**Please submit the name of 'Your Choice' via Canvas by 13 September.** If it will help you decide you can watch the trailers by searching for the movie on [IMDB](https://www.imdb.com/) or [YouTube](https://www.youtube.com/). 

**How/Where to Watch:** Most of the films are available via the UF Library access to Kanopy, other free streaming platforms, or as DVDs that can be checked out from the UF Library's Course Reserves. A few of them are only available on subscription-based streaming platforms such as Netflix or Amazon, but _there are plenty of movies that do not require subscriptions or paying for a rental._ **_Do not spend any personal funds on this assignment._**  

<!-- |**Platforms streaming free movies:**| | -->
<!-- |:----|:------| -->
<!-- |[Tubi](https://tubitv.com/)|[Kanopy](https://www.kanopy.com/)| -->
<!-- |[Plex](https://www.plex.tv/)|[YouTube](https://www.youtube.com/)| -->
<!-- |[Crackle](https://www.crackle.com/)|[Pluto TV](https://pluto.tv/en)| -->
<!-- |[Film Detective](https://www.thefilmdetective.com/)|[YuppTV](https://www.yupptv.com/)| -->
<!-- |[IMDB](https://www.imdb.com/)|[Digitalia](https://www.digitaliafilmlibrary.com/)| -->
**Many of the movies can be streamed for free at one of the following online channels:**  

   > * [Tubi](https://tubitv.com/)
   > * [Kanopy](https://www.kanopy.com/)
   > * [Plex](https://www.plex.tv/)
   > * [YouTube](https://www.youtube.com/)
   > * [Crackle](https://www.crackle.com/)
   > * [Pluto TV](https://pluto.tv/en)
   > * [YuppTV](https://www.yupptv.com/)
   > * [IMDB](https://www.imdb.com/)
   > * [Film Detective](https://www.thefilmdetective.com/)
   > * [Digitalia](https://www.digitaliafilmlibrary.com/) 


**Important Content Warning**: The some of the assigned films contain strong language, nudity, sexual situations, and violence, including sexual assault. There may be dialogue about or depictions of race, class, gender, sexuality, or other topics that are uncomfortable, disturbing, or offensive. Analyzing these depictions and their broader cultural implications is an important part of this assignment, so I encourage you to prepare yourself for this possibility. However, if you are concerned that you will find the content of the films you have been assigned to be difficult or even traumatic, please let me know so we can arrange an alternative film for you to review. You do *not* have to tell me why you want to switch, only that you would prefer to be assigned another film. 

**Language:** Some of the films may be partially or entirely in languages other that English and require subtitles. 

**Extra Credit**: Remember what I said about value judgments? Well...let's just put that aside for a moment to say there are some movies that are so ridiculously bad that I will award 10 points of extra credit simply for selecting one of them for your 3rd review. 

## Submission Requirements and Rubric
\vspace{0.3cm}
**For _each_ film you must submit the following:**

1. A completed 'Tropical Trope Checklist', and

1. Your analysis of how the use of these tropes reinforces or subverts our perception of rain forests and the people living in   them (min. 350 words each; 350 words is approx. 1/2 page of single space, 12 pt. text).

**Assignment Submission: ** Files uploaded via Canvas. Your three essays must be submitted as a single MS Word document or PDF file (file extensions .doc, .docx, or .pdf). Your trope checklist must be uploaded as a Microsoft Excel file (file extension .xls or .xlsx file).

**Assignment value: ** 100 points

**Due Date: ** All reviews are due October 4^th^ by 5 pm.  

**Required Content & Grading Rubric**: The review & checklists will be evaluated using the point values and minimum standards in the rubric below. _Note that the rubric on Canvas lists additional 'outcomes' to be evaluated. These additional criteria will **_not_** be used to grade your assignment. These are some things the Quest Program is asking us to evaluate internally. Your assignment will be graded **solely** with the rubric in the table below._ 

<!-- The individual components will be evaluated as: -->

<!-- 1. "Exceeds required standards": Essay is of the required length with thorough and well-reasoned arguments and several specific examples as supporting evidence;engaging conclusion that summarizes the evidence and connects to the thesis and body. The examples accurate and the writing is articulate and sophisticated, with few grammatical mistakes or spelling errors. Overall, the paper is well written. Each checklist records 10 or more examples with a time stamp for each event.  -->

<!-- 2. "Meets the minimum standards: Essay is of the required length; generally sound argument with some evidence in support of arguments but lacking details or explanation. There are some grammatical mistakes or spelling errors but the paper is henerally well written. The checklist includes 5-10 examples and is mostly complete; some time stamps or other details missing.  -->

<!-- 3. "Incomplete / Unacceptable": The paper is well short of the required length or poorly organized; arguments are poorly articulated; examples in support of the argument are few or poorly chosen. Multiple grammatical and spelling errors. Checklist incomplete (<5 examples for each, few or no time stamps).  -->

&nbsp;   

<!-- \begin{landscape} -->
```{r rubric, echo=FALSE,message = FALSE,warning=FALSE}

section <- data.frame(section = c("Essay","", "Checklist"))

pts<-data.frame(pts=c("70","","30"))
                   
exceeds <- data.frame(exceeds = c("Essays are of the required length. One or more historical narratives about rain forests are identified; well-reasoned arguments for how the film promotes or subverts these narratives are backed up by specific examples. An engaging conclusion summarizes the evidence and connects it back to the central thesis. The writing is clear, with few grammatical mistakes or spelling errors. Overall, the paper is well written. \\textbf{(70-63 pts)}","","The film's checklist records 10 or more tropes with a time stamp and description of the event for each one. \\textbf{(9-10 pts)}"))

meets <- data.frame(meets = c("Essays are somewhat shorter than the required length; a historical narrative is identified but the supporting argument is unclear or backed up by weak or limited supporting evidence. The paper is generally well written but there are some grammatical or spelling errors. \\textbf{(62-49 pts)}","","The checklist for a film includes 5-9 tropes and is mostly complete; some time stamps or other details missing. \\textbf{(7-8 pts)}"))

dnm <- data.frame(dnm = c("The essays are much shorter than the required length; no historical narrative is identified or if one is, the arguments in support are poorly articulated or the supporting examples are limited or poorly chosen. Multiple grammatical or spelling errors. \\textbf{(<48 pts)}","","The checklist for a film is incomplete (<5 examples for each), or few / no time stamps or additional information. \\textbf{(<6 pts)}"))

rubric<-bind_cols(section,pts,exceeds,meets,dnm)

names(rubric)<-c("Section","Max. Points","Exceeds Expectations","Meets Expectations","Below Expectations")
kable(rubric, 
  align = "cclll", 
  # format = "html", 
  format = "latex", 
  row.names = FALSE, 
  booktabs = T, 
  escape=F,
  linesep = "" 
) %>% 
  # row_spec(2, hline_after = TRUE) %>% -->
  # column_spec(3:7, width = "2.5cm") %>%  #removes the blank line after every 5 lines) %>%
  kable_styling( 
    position = "left",
    bootstrap_options = c("hover"),
    latex_options = c("scale_down")
  ) %>%  
    column_spec(1, width = "5em") %>% 
  column_spec(2, width = "2em") %>% 
  column_spec(3, width = "15em") %>%
   column_spec(4, width = "15em") %>%
  column_spec(5, width = "15em")
```

<!-- ## Assigned Movies -->
<!-- \vspace{0.3cm} -->

<!-- \begin{landscape} -->

<!-- ```{r movie_table, echo=FALSE,message = FALSE,warning=FALSE} -->
<!-- movies <- readxl::read_excel("movies.xlsx") %>% -->
<!--   unite("subscription", paramount:apple, remove = TRUE, sep = ",") %>% -->
<!--   unite("free", kanopy:other_free, remove = TRUE, sep = ",") %>% -->
<!--   arrange(year,movie) %>% -->
<!--   filter(is.na(cat)) %>%  -->
<!--   # filter(cat!="assigned") %>% -->
<!--   mutate(`ID No.` = row_number(), .before=movie) %>%  -->
<!--   select(-cat, -->
<!--          -Notes) %>%  -->
<!--   mutate(`Extra Credit` = replace_na(`Extra Credit`,"")) -->


<!-- movies$subscription <- gsub("NA,", "", movies$subscription) -->
<!-- movies$subscription <- gsub(",NA", "", movies$subscription) -->
<!-- movies$subscription <- gsub(",", ", ", movies$subscription) -->



<!-- movies$free <- gsub("NA,", "", movies$free) -->
<!-- movies$free <- gsub(",NA", "", movies$free) -->
<!-- movies$free <- gsub(",", ", ", movies$free) -->
<!-- movies$free <- gsub(";", ",", movies$free) -->
<!-- movies$free <- gsub("_free", "", movies$free) -->
<!-- # -->
<!-- # movies <- movies %>% -->
<!-- #   mutate(across(everything(), ~replace_na(.x, ""))) -->

<!-- movies$subscription <- gsub("NA", "", movies$subscription) -->
<!-- movies$free <- gsub("NA", "", movies$free) -->
<!-- movies$subscription <- gsub("_", " ", movies$subscription) -->
<!-- movies$free <- gsub("_", " ", movies$free) -->

<!-- movies <- movies %>% -->
<!--   rename( -->
<!--     "Free" = "free", -->
<!--     "Year" = "year", -->
<!--     "Paid" = "subscription", -->
<!--     "Title" = "movie", -->
<!--     "Summary" = "summary" -->
<!--   ) %>% -->
<!--   relocate(Year, .after = Title) %>% -->
<!--   mutate(Free = str_to_title(Free)) %>% -->
<!--   mutate(Paid = str_to_title(Paid)) -->

<!-- movies$Free <- gsub("Dvd", "DVD", movies$Free) -->
<!-- movies$Free <- gsub("Youtube", "YouTube", movies$Free) -->
<!-- movies$Free <- gsub("Imdb2", "IMDB", movies$Free) -->

<!-- movies$Paid <- gsub("Hbo", "HBO", movies$Paid) -->

<!-- # kbl(movies, -->
<!-- #       # digits = 2, -->
<!-- #       longtable=TRUE, -->
<!-- #       align="l", -->
<!-- #       format="latex", -->
<!-- #       row.names = FALSE, -->
<!-- #       escape= T, -->
<!-- #       booktabs=T, -->
<!-- #       linesep = "", -->
<!-- #       ) %>% -->

<!-- kable(booktabs = TRUE, -->
<!--       # movies, "html", -->
<!--       movies, "latex", -->
<!--       align="clclllc", -->
<!--   # caption = "Test", -->
<!--   longtable = TRUE -->
<!-- ) %>% -->

<!--   # FOR HTML -->
<!--     #  kable_styling( -->
<!--   #   position = "left", -->
<!--   #   bootstrap_options = c("hover","striped"), -->
<!--   #   latex_options = c("scale_down") -->
<!--   # ) %>% -->
<!-- # FOR PDF -->
<!--   kable_paper("striped", -->
<!--     latex_options = c("hold_position", "repeat_header", "scale_down"), -->
<!--     font_size = 9) %>% # USE for PDF -->
<!--     # font_size = 14) %>% -->
<!--   # pack_rows("Required", 1, 4, label_row_css = "background-color: #483D8B; color: #fff;") %>% -->
<!--   # pack_rows("Choose 1 + Assigned 1", 5, 42, label_row_css = "background-color: #483D8B; color: #fff;") %>% -->
<!--   # pack_rows("Extra Credit", 43, 52, label_row_css = "background-color: #483D8B; color: #fff;") %>% -->
<!--   column_spec(1, width = "3em") %>% -->
<!--   column_spec(2, width = "15em") %>% -->
<!--   column_spec(3, width = "3em") %>% -->
<!--   column_spec(4, width = "25em") %>% -->
<!--   column_spec(5, width = "5em") %>% -->
<!--   column_spec(6, width = "5em") %>% -->
<!--   column_spec(7, width = "8em") %>% -->
<!--   #   # column_spec(4:6, width = "4em") %>% -->
<!--   # #   column_spec(4, width = "3em") -->
<!--   # #   row_spec(0,hline_after = F, bold=T) %>% -->
<!--   # #   row_spec(c(1:5),hline_after = T) %>% -->
<!--   row_spec(1:nrow(movies)-1, hline_after = TRUE) %>% -->
<!--   row_spec(0, bold = T, color = "#483D8B", hline_after = F)  -->
<!--   # row_spec(42, hline_after = T) %>% -->
<!--   # row_spec(4, hline_after = T) -->
<!-- #   add_indent(6) -->
<!-- ``` -->
<!-- \end{landscape} -->
