---
title: "IDS 2935: Course Introduction"
author: "Emilio M. Bruna"
date: "updated: `r Sys.Date()`"
mainfont: SourceSansPro
geometry: margin=1in
fontsize: 12pt
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[R]{last update `r Sys.Date()`}
- \fancyfoot[C]{ }
- \fancyhead[R]{Course Introduction, p. \thepage}
- \fancyhead[L]{IDS 2935 - Rain Forests (`r format(Sys.time(), '%Y')`)}
- \usepackage[default]{sourcesanspro}
- \usepackage{parskip}
- \usepackage{xcolor}
- \AtBeginDocument{\let\maketitle\relax}
- \usepackage{sectsty} \sectionfont{\centering}
- \usepackage{titlesec}
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
- \usepackage{sectsty} \subsectionfont{\color{darkmidnightblue}}
- \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
output:
  pdf_document: default
  html_document:
    df_print: paged
  rmdformats::robobook: default
editor_options: 
  markdown: 
    wrap: 72
---
```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

# IDS 2935: Course Introduction

## Before Class
1.  Prepare survey and post as Assignment 1

1. Email students: 

>Hi Everyone,
>
>I’m your instructor for "IDS 2935: The Future of Rain Forests". This is just a reminder that the first class session is tomorrow (Thursday) from 9:35-11:30 AM in MAEB-0211. 
>
>I've posted some information to the course Canvas page, including the syllabus and an overview of the course - both of which we will be going over tomorrow.  I have also posted >"Assignment 1" - a very short survey that should take you just a few minutes (if you aren't able to complete it in advance we will have a few minutes in class for you to do so).   
>
>To log on to the Canvas page:  1)  Go to the e-Learning website 2)  Choose “Log into e-Learning” and log in with your Gatorlink username and password. 3)  Click on“Courses” at the top of the page 4)  Choose this course:  [IDS 2935] from the list  5) Complete Assignment 1 
>
>If you have trouble logging into the E-learning system, contact: helpdesk@ufl.edu or call (352) 392-4357.
>
>See you all tomorrow!
>
>Emilio Bruna


## Bring to Class

1. Roster
1. Name cards & Markers
1. Syllabi
1. Chocolates
1. Masks, Hand Sanitizer
1. PDF of class outline

<!-- **<<Revision for v 2.0: have 1/2 the class do the survey for "tropical rain forest" and the other half do the words that come to mind with "jungle" - would be really interesteing to compare the differences that come to mind, and is a good lead-in to Jungle being defined by the British officers.">>**  -->

## Pre-class Preparation (Students)

1. **Assignments:** Complete the survey if they have an opportunity to do so
2. **Readings & Videos:** None

## Session Objectives & Competencies:   

1. Introduce the class and challenges of tropical rain forest conservation 
2. Review the Syllabus
3. Become familiar with students, their concerns, and their interests


\newpage
```{r timer, echo=FALSE}

Block1_intro <- 10
Block1_breakout <- 10
Break <- 0
return_results <- 10
intro_next_session <- 20
questions <- 5  
  
total_time <- 
  Block1_intro + 
  Block1_breakout + 
  Break + 
  return_results + 
  questions +
  intro_next_session 


time_remain <- 50 - total_time
```
# Class Outline (Total Time: `r total_time` min)
\vspace{0.5cm}
### **Topic 1: Survey** (`r Block1_intro` min)

* Respond to the survey (includes free-listing words that come to mind when hearing the words "Tropical Rain Forest").

### **Breakout** (`r Block1_breakout` min)

* Introduce yourselves to each other (name, major, where from), and without looking at your cell phones or computers see if you can answer this question:  

> 1. What is the primary ingredient in Chocolate?
> 1. What THREE countries are the primary producers of this ingredient?   

### Return and discuss breakout results (`r return_results` min)

* **Review the answers**  

> 1. Main Ingredient: Cacao
> 1. Primary producers 3 countries produce ~70% of world's Cacao  
>     #1. Ivory Coast:  ~2,200,000 metric tons (46%)  
>     #2. Ghana: ~820,000 metric tons (17%)  
>     #3. Ecuador ~370,000 metric tons (6%)
> 1. World's leading consumer of cacao products: USA (797,000 tons in 2021)


* **Why Cacao?** Cacao is a perfect example of the challenges faced when considering the Future of Rain Forests  

> 1. Hugely important crop at the macroeconomic (major national export for many countries, multibillion dollar industry) and microeconomic level (major source of family income)
> 1. Threatened by climate change
> 1. Increasing global demand has major consequences for rain forests  

* We're going to study these challenges and consider - and maybe even come up with - the potential soluctions to them.

### Course Overview  (`r intro_next_session` min)      

> **Syllabus / Course overview**

> 1. Most of the course work is in-class. Remind people this course is still a bit of an experiment, and also that...  
> 1. Current events (e.g., deforestation, fires, national or international election results) so there will be some changes on the fly. Check the syllabus frequently.  
> 1. "Some of you may be new to UF and so may not know what Office Hours are. They're an opportunity to..."  
> 1. "This class has a very reasonable amount of homework and reading and _no tests_. In return I ask that you come to class committed to engage and enjoy yourself. This class will (I hope) be the least stressful one you have all semester. That doesn't necessarily mean it will be the easiest - in fact it may be quite challenging sometimes - but I hope that won't be too stressful. That's my commitment to you."


### Closing Remarks/Questions (`r questions` min)

> 1. Don't forget Fill out the Survey in Canvas as Assignment 1!

\vspace{1.5cm}
# Additional Resources and Reading
\vspace{0.5cm}
1. [The Real Price of a Chocolate Bar: West Africa’s Rainforests - Yale e360](https://e360.yale.edu/features/the-real-price-of-a-chocolate-bar-west-africas-rainforests)
2. [Ghana Exports](https://tradingeconomics.com/ghana/exports-by-category)
3. [Ivory Coast Exports](https://tradingeconomics.com/ivory-coast/exports-by-category)
4. Leading Cocoa Exporters: [[link-1]](https://www.kakaoplattform.ch/about-cocoa/cocoa-facts-and-figures) [[link-2]](https://www.statista.com/statistics/1112357/global-leading-exporters-of-cocoa-bean) [[link-3]](https://worldpopulationreview.com/country-rankings/cocoa-producing-countries)
5. Cocoa/Chocolate Market  [[link]](https://www.fortunebusinessinsights.com/industry-reports/cocoa-and-chocolate-market-100075)
6. US Chocolate sales [[link]](https://www.axios.com/2022/03/18/chocolate-and-candy-sales-hit-a-record)

