---
title: "Assignment 1 - Movie Reviews"
author: "Emilio M. Bruna"
date: "`r format(Sys.time(), '%Y')`"
web: www.BrunaLab.org
github: embruna
twitter: https://twitter.com/BrunaLab
phone: (352) 514-3935
email: embruna@ufl.edu
geometry: margin=1in
fontsize: 12pt
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
site: bookdown::bookdown_site
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \fancyhead[R]{Assignment 1 - Movie Reviews, p. \thepage}
- \fancyhead[L]{IDS 2935 - Rain Forests (`r format(Sys.time(), '%Y')`)}
- \usepackage[default]{sourcesanspro}
- \usepackage{parskip}
- \usepackage{xcolor}
- \usepackage{lscape}
- \AtBeginDocument{\let\maketitle\relax}
# - \usepackage{sectsty} \allsectionsfont{\raggedright}
- \usepackage{sectsty} \sectionfont{\centering}
- \usepackage{titlesec}
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
- \usepackage{sectsty} \subsectionfont{\centering\color{darkmidnightblue}}
- \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
always_allow_html: true
# classoption: landscape
output: pdf_document
# output: html_document
  # word_document: default
# output: html_document
# weight: 5
    # df_print: paged
---


```{r setup_syllabus, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(here)
```
# Tropical Tropes in Movies 
\vspace{0.5cm}
## Project Overview
\vspace{0.3cm}
Your assignment is to watch **three** films set in tropical rain forests and study how the rain forests are presented, how the rain forest setting influences character development, and how the rain forest and the situations encountered there by characters help advance the films' narrative. Your review should not be a summary of the film and it's plot (i.e., it is not a *descriptive review*), nor a judgment regarding whether the film is "good" or "bad" (i.e., it is not an *evaluative review*). **Your objective is to analyze and compare:** 

1. How the rain forest setting underscores the film's major themes 
2. How the film reinforces or subverts stereotypes (i.e., tropes) about rain forests and the people that live in them
3. How the depiction of rain forests in the film compares with what you have learned about rain forests in class. 

You must support your claims with specific examples drawn from the major elements below. **As you screen each movie, record your observations and fill out the Movie Trope Checklist.**

* **Plot**: the narrative, setting, key events, action sequences, resolution, plausibility, themes, cultural context, etc. 
* **Characters and their development**: professions, personality, motivation, interactions, response to rain forest setting, etc.
* **Visuals**: scenery, flora & fauna, props, wardrobe, shots, perspective, lighting, editing, effects, etc.
* **Sound**: background sounds, use and timing of sound vs silence, musical score, songs, etc.


## Film Selection
\vspace{0.3cm}
**Everyone will watch and review three movies:**

1. _Aguirre, Wrath of God_ (1972, directed by Werner Herzog, Rotten Tomatoes: 96%)
1. _Anaconda_ (1997, directed by Luis LLosa, Rotten Tomatoes: 40%)
1. A movie from the list below - your choice

<!-- * Fern Gully: The Last Rainforest OR Avatar -->

**Please submit the name of 'Your Choice' via Canvas by 8 September.** If it will help you decide you can watch the trailers by searching for the movie on [IMDB](https://www.imdb.com/) or [YouTube](https://www.youtube.com/). 

**How/Where to Watch:** Most of the films are available via the UF Library access to Kanopy, other free streaming platforms, or as DVDs that can be checked out from the UF Library's Course Reserves. A few of them are only available on subscription-based streaming platforms such as Netflix or Amazon, but _there are plenty of movies that do not require subscriptions or paying for a rental._ **_Do not spend any personal funds on this assignment._**  

<!-- |**Platforms streaming free movies:**| | -->
<!-- |:----|:------| -->
<!-- |[Tubi](https://tubitv.com/)|[Kanopy](https://www.kanopy.com/)| -->
<!-- |[Plex](https://www.plex.tv/)|[YouTube](https://www.youtube.com/)| -->
<!-- |[Crackle](https://www.crackle.com/)|[Pluto TV](https://pluto.tv/en)| -->
<!-- |[Film Detective](https://www.thefilmdetective.com/)|[YuppTV](https://www.yupptv.com/)| -->
<!-- |[IMDB](https://www.imdb.com/)|[Digitalia](https://www.digitaliafilmlibrary.com/)| -->
**Many of the movies can be streamed for free at one of the following online channels:**  

   > * [Tubi](https://tubitv.com/)
   > * [Kanopy](https://www.kanopy.com/)
   > * [Plex](https://www.plex.tv/)
   > * [YouTube](https://www.youtube.com/)
   > * [Crackle](https://www.crackle.com/)
   > * [Pluto TV](https://pluto.tv/en)
   > * [YuppTV](https://www.yupptv.com/)
   > * [IMDB](https://www.imdb.com/)
   > * [Film Detective](https://www.thefilmdetective.com/)
   > * [Digitalia](https://www.digitaliafilmlibrary.com/) 


**Important Content Warning**: The some of the assigned films contain strong language, nudity, sexual situations, and violence, including sexual assault. There may be dialogue about or depictions of race, class, gender, sexuality, or other topics that are uncomfortable, disturbing, or offensive. Analyzing these depictions and their broader cultural implications is an important part of this assignment, so I encourage you to prepare yourself for this possibility. However, if you are concerned that you will find the content of the films you have been assigned to be difficult or even traumatic, please let me know so we can arrange an alternative film for you to review. You do *not* have to tell me why you want to switch, only that you would prefer to be assigned another film. 

**Language:** Some of the films may be partially or entirely in languages other that English and require subtitles. 

**Extra Credit**: Remember what I said about value judgments? Well...let's just put that aside for a moment to say there are some movies that are so ridiculously bad that I will award 10 points of extra credit simply for selecting one of them for your 3rd review. 

## Submission Requirements and Rubric
\vspace{0.3cm}
**For each film you must submit the following:**

1. Your critical analysis and cross-movie comparison (500-700 words)
2. A completed 'Movie Trope Checklist' for each film

**Assignment Submission: ** files uploaded via Canvas.  

**Assignment value: ** 100 points

**Due Date: ** All reviews are due October 4^th^ by 5 pm.  

**Required Content & Grading Rubric**: The review & checklists will be evaluated using the point values and minimum standards in the rubric below. 
<!-- The individual components will be evaluated as: -->

<!-- 1. "Exceeds required standards": Essay is of the required length with thorough and well-reasoned arguments and several specific examples as supporting evidence;engaging conclusion that summarizes the evidence and connects to the thesis and body. The examples accurate and the writing is articulate and sophisticated, with few grammatical mistakes or spelling errors. Overall, the paper is well written. Each checklist records 10 or more examples with a time stamp for each event.  -->

<!-- 2. "Meets the minimum standards: Essay is of the required length; generally sound argument with some evidence in support of arguments but lacking details or explanation. There are some grammatical mistakes or spelling errors but the paper is henerally well written. The checklist includes 5-10 examples and is mostly complete; some time stamps or other details missing.  -->

<!-- 3. "Incomplete / Unacceptable": The paper is well short of the required length or poorly organized; arguments are poorly articulated; examples in support of the argument are few or poorly chosen. Multiple grammatical and spelling errors. Checklist incomplete (<5 examples for each, few or no time stamps).  -->


&nbsp;   

<!-- \begin{landscape} -->
```{r rubric, echo=FALSE,message = FALSE,warning=FALSE}

section <- data.frame(section = c("Essay","", "Checklist"))

pts<-data.frame(pts=c("70","","30"))
                   
exceeds <- data.frame(exceeds = c("Essay is of the required length with thorough and well-reasoned arguments and several specific examples as supporting evidence;engaging conclusion that summarizes the evidence and connects to the thesis and body. The examples accurate and the writing is articulate and sophisticated, with few grammatical mistakes or spelling errors. Overall, the paper is well written. \\textbf{(70-63 pts)}","","Each checklist records 10 or more examples with a time stamp for each event. \\textbf{(9-10 pts)}"))

meets <- data.frame(meets = c("Essay is of the required length; generally sound argument with some evidence in support of arguments but lacking details or explanation. There are some grammatical mistakes or spelling errors but the paper is henerally well written. \\textbf{(62-49 pts)}","","The checklist includes 5-10 examples and is mostly complete; some time stamps or other details missing. \\textbf{(7-8 pts)}"))

dnm <- data.frame(dnm = c("The paper is well short of the required length or poorly organized; arguments are poorly articulated; examples in support of the argument are few or poorly chosen. Multiple grammatical and spelling errors. \\textbf{(<48 pts)}","","Checklist incomplete, with <5 examples for each, or few / no time stamps. \\textbf{(<6 pts)}"))

rubric<-bind_cols(section,pts,exceeds,meets,dnm)

names(rubric)<-c("Section","Max. Points","Exceeds Expectations","Meets Expectations","Below Expectations")
kable(rubric, 
  align = "cclll", 
  # format = "html", 
  format = "latex", 
  row.names = FALSE, 
  booktabs = T, 
  escape=F,
  linesep = "" 
) %>% 
  # row_spec(2, hline_after = TRUE) %>% -->
  # column_spec(3:7, width = "2.5cm") %>%  #removes the blank line after every 5 lines) %>%
  kable_styling( 
    position = "left",
    bootstrap_options = c("hover"),
    latex_options = c("scale_down")
  ) %>%  
    column_spec(1, width = "5em") %>% 
  column_spec(2, width = "2em") %>% 
  column_spec(3, width = "15em") %>%
   column_spec(4, width = "15em") %>%
  column_spec(5, width = "15em")
```

<!-- \end{landscape} -->
<!-- ```{r rubric, echo=FALSE,message = FALSE,warning=FALSE} -->
<!-- section <- data.frame(Section = c("Critical Analysis", "Checklist 1","Checklist 2","Checklist 3", "Total")) -->
<!-- section_points <- data.frame(section_points = c(70, 10,10,10)) -->

<!-- Cat1_bottom <- round(section_points * .9, 0) -->
<!-- Cat2_bottom <- round(section_points * .7, 0) -->
<!-- Cat3_bottom <- round(section_points * .6, 0) -->
<!-- # Cat4_bottom <- round(section_points*.5,0) -->
<!-- # Cat5_bottom <- round(section_points*.4,0) -->
<!-- # Exceptional <- floor(section_points*0.1) -->

<!-- points <- bind_cols( -->
<!--   section_points, -->
<!--   section_points, Cat1_bottom, -->
<!--   Cat1_bottom-1, Cat2_bottom, -->
<!--   Cat2_bottom-1, Cat3_bottom -->
<!-- ) -->
<!-- # Cat3_bottom-1,Cat4_bottom, -->
<!-- # Cat4_bottom-1,Cat5_bottom, -->
<!-- # Exceptional) -->
<!-- points <- bind_rows(points, colSums(points)) -->

<!-- totals <- bind_cols(section, points) %>% -->
<!--   rename("Value" = `section_points...2`) %>% -->
<!--   mutate( -->
<!--     `Exceeds standards` = -->
<!--       paste(`section_points...3`, `section_points...4`, sep = "-"), -->
<!--     .keep = "unused" -->
<!--   ) %>% -->
<!--   mutate( -->
<!--     `Meets standards` = -->
<!--       paste(`section_points...5`, `section_points...6`, sep = "-"), -->
<!--     .keep = "unused" -->
<!--   ) %>% -->
<!--   mutate( -->
<!--     `Below standards` = -->
<!--       # paste(`section_points...7`, `section_points...8`, sep = "-"), -->
<!--     paste("<",`section_points...7`,sep = " "), -->
<!--     .keep = "unused" -->
<!--   ) %>%  -->
<!--   select(-`section_points...8`) %>%  -->
<!--   filter(Section!="Total") -->

<!-- # %>% -->
<!-- #   mutate(`Incomplete / Unacceptable` = -->
<!-- #            paste(`section_points...9`,`section_points...10`,sep="-"), -->
<!-- #          .keep="unused") %>% -->
<!-- #   rename(`Potential Bonus` = `section_points...11`) %>% -->
<!-- #   select(Section, Value, `Meets standards`, `Moderate revisions`, `Major revisions`, `Incomplete / Unacceptable`,`Potential Bonus`) -->

<!-- # -->
<!-- # -->
<!-- # totals[5,3:6]<-"" -->



<!-- kable(totals, -->
<!--   align = "lcccc", -->
<!--   # format = "html", -->
<!--   format = "latex", -->
<!--   row.names = FALSE, -->
<!--   booktabs = T, -->
<!--   linesep = "" -->
<!-- ) %>% -->
<!--   # row_spec(2, hline_after = TRUE) %>% -->
<!--   # column_spec(3:7, width = "2.5cm") %>%  #removes the blank line after every 5 lines) %>% -->
<!--   kable_styling( -->
<!--     position = "left", -->
<!--     bootstrap_options = c("hover"), -->
<!--     latex_options = c("scale_down") -->
<!--   ) %>%  -->
<!--     column_spec(2, width = "5em") %>%  -->
<!--   column_spec(3, width = "11em") %>%  -->
<!--    column_spec(4, width = "10em") %>%  -->
<!--   column_spec(5, width = "11em")  -->
<!-- # , -->
<!-- #                  full_width = T, -->
<!-- ``` -->
<!-- \newpage -->
<!-- \blandscape -->
## Movies
<!-- \vspace{0.3cm}  -->
<!-- ```{r data_locator, echo=FALSE,message = FALSE,warning=FALSE} -->

<!-- ``` -->

\begin{landscape}
```{r movie_table, echo=FALSE,message = FALSE,warning=FALSE}
movies <- readxl::read_excel("movies.xlsx") %>%
  unite("subscription", paramount:apple, remove = TRUE, sep = ",") %>%
  unite("free", kanopy:other_free, remove = TRUE, sep = ",") %>%
  filter(is.na(cat) == FALSE) %>%
  filter(cat != "cut") %>%
  filter(cat != "rent") %>%
  mutate_at(c("cat"), str_replace_all, pattern = "pay stream", replacement = "Your choice (subscription req.)") %>%
  mutate_at(c("cat"), str_replace_all, pattern = "[2,3]", replacement = "Your choice (free)") %>%
  mutate_at(c("cat"), str_replace_all, pattern = "4", replacement = "Extra Credit") %>%
  mutate_at(c("cat"), str_replace_all, pattern = "1", replacement = "Required")



movies$cat <- as.factor(movies$cat)
movies$cat <- fct_relevel(movies$cat, "Required", "Your choice (free)", "Your choice (subscription req.)", "Extra Credit")

movies <- movies %>%
  arrange(cat, movie) %>%
  # select(-trailer_for_class,-Notes)
  select(-trailer_for_class, -Notes)




movies$subscription <- gsub("NA,", "", movies$subscription)
movies$subscription <- gsub(",NA", "", movies$subscription)
movies$subscription <- gsub(",", ", ", movies$subscription)



movies$free <- gsub("NA,", "", movies$free)
movies$free <- gsub(",NA", "", movies$free)
movies$free <- gsub(",", ", ", movies$free)
movies$free <- gsub(";", ",", movies$free)
movies$free <- gsub("_free", "", movies$free)
#
# movies <- movies %>%
#   mutate(across(everything(), ~replace_na(.x, "")))

movies$subscription <- gsub("NA", "", movies$subscription)
movies$free <- gsub("NA", "", movies$free)
movies$subscription <- gsub("_", " ", movies$subscription)
movies$free <- gsub("_", " ", movies$free)

movies <- movies %>%
  rename(
    "Free" = "free",
    "Year" = "year",
    "Paid" = "subscription",
    "Category" = "cat",
    "Movie" = "movie",
    "Summary" = "summary"
  ) %>%
  select(-Category) %>%
  relocate(Year, .after = Movie) %>%
  mutate(Free = str_to_title(Free)) %>%
  mutate(Paid = str_to_title(Paid))

movies$Free <- gsub("Dvd", "DVD", movies$Free)
movies$Free <- gsub("Youtube", "YouTube", movies$Free)
movies$Free <- gsub("Imdb2", "IMDB", movies$Free)

# kbl(movies,
#       # digits = 2,
#       longtable=TRUE,
#       align="l",
#       format="latex",
#       row.names = FALSE,
#       escape= T,
#       booktabs=T,
#       linesep = "",
#       ) %>%

kable(booktabs = TRUE,
      # movies, "html",
      movies, "latex",
  # caption = "Test",
  longtable = TRUE
) %>%

  # FOR HTML
    #  kable_styling(
  #   position = "left",
  #   bootstrap_options = c("hover","striped"),
  #   latex_options = c("scale_down")
  # ) %>%
# FOR PDF
  kable_paper("striped",
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 9) %>% # USE for PDF
    # font_size = 14) %>%
  pack_rows("Required", 1, 2, label_row_css = "background-color: #483D8B; color: #fff;") %>%
  pack_rows("Choose 1", 3, 77, label_row_css = "background-color: #483D8B; color: #fff;") %>%
  pack_rows("Extra Credit", 78, 84, label_row_css = "background-color: #483D8B; color: #fff;") %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "30em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "6em") %>%
  #   # column_spec(4:6, width = "4em") %>%
  # #   column_spec(4, width = "3em")
  # #   row_spec(0,hline_after = F, bold=T) %>%
  # #   row_spec(c(1:5),hline_after = T) %>%
  row_spec(0, bold = T, color = "#483D8B", hline_after = F) %>%
  row_spec(77, hline_after = T) %>%
  row_spec(2, hline_after = T)
#   add_indent(6)
```
\end{landscape}